### 2015-03-18 paper_40_cri.tex
updates through chapter 4

    The scores for CRI will range from -1, indicating the worst 
    performance, all the way to +1, indicating perfection.
    A score of 0 is an indication of meeting the basic expectations. 
    A negative score indicates under-performance and a 
    positive score indicates over-performance.   Here are some 
    examples. An CRI score of 0.35 means the organization is 
    performing 35\% better than expected.  Conversely, a score 
    of -0.15 means an organization is performing 15\% worse than expected.

    Below are the attributes of the CRI scoring.
    \begin{itemize}
        \item The range of scores must have equal values above and below 0
        \item The minimum score must equate to the worst possible 
            performance, however that is defined
        \item Similarily, the maximum score must equate to the best possible performance.  
        \item A score of 0 must be average (or expected) performance
        \item All individual elements must have the same scoring range
    \end{itemize}

@@

    \subsection{ELEMENTS OF CRI}
        Each of the 5 elements of CRI has its own set of data that needs to
        be collected and a formula for calculating a score. 
        These five elements will be outline in the next sections.

@@

            \paragraph{QUALITY DATA}
                In order to properly score the quality of an SDO,
                certain data needs to be obtained in order to measure
                performance. Table \ref{tab:qualitydata} identifies
                the columns of data that will be used to create
                a score for the quality element of CRI.  
                Each column is classified as \textit{required} or
                \textit{optional}.  That is to allow some flexibility
                in the model for organizations that collect
                varying amounts of data.

@@

                The development and testing effort can come from any of 
                the following choices for effort. It is possible
                that other measures will work for effort.
                \begin{description}
                    \item[Actual Time] This number is a representation of the 
                        total amount of time spent on a project.  This number
                        can be measured in any unit of time: hours, days, weeks,
                        etc.  Actual time can be applied to development or testing
                        effort.
                    \item[Estimated Time] This number is a representation of the 
                        initial estimated amount of time spent on a project.  This number
                        can be measured in any unit of time: hours, days, weeks,
                        etc.  Estimated time can be applied to development or testing
                        effort.  It is common for the estimated and actual times
                        to be diffent.
                    \item[SLOC]  This number is the count of 
                        the total number of lines of source code for a project. 
                        Obviously, 
                        this item only counts as a level of
                        effort for development unless coding in used to generate
                        automated test cases. \footnote{Automated testing is the
                        process of creating software to automatically run tests
                        against other software.  The adoption of automated testing
                        is varied and it is not a solution in all cases 
                        \cite{Ramler2006}. }
                    \item[Modified Lines Of Code] This number is a count of the number 
                        of modified lines of source code. Modified lines is 
                        defined as the number of deleted, added, and modified 
                        lines of source code.  This number is different from above
                        since it does not include all the lines of source code.  Similar
                        to above, this number makes more sense for development effort.
                    \item[Test Cases] A test case is a step or series of steps followed
                        to validate some expected outcome of software.  Organizations
                        will create a number of test cases to be validated for a
                        software system.  The number of such test cases could
                        be used as a level of testing effort.
                \end{description}

@@

            \paragraph{QUALITY FORMULA}
                The first step in creating a score for the quality
                element is analysis of the historical data to create
                a baseline function.  The historical
                data is all quality data collected before  a given point
                in time.  Some common historical cutoffs are the current date
                or the end of the previous fiscal year.  Then a mathematical
                model, called the \textit{baseline quality function},
                to predict PROD Defects will be produced.  In statistical
                terms, the response is \textit{PROD Defects} and the predictors
                are: \textit{UAT Defects}, \textit{SIT Defects}, 
                \textit{Testing Effort}, and \textit{Development Effort}.  
                Some of the following strategies will be employed to find 
                a reasonable model.
                \begin{itemize}
                    \item Removal of outliers and/or influential points
                    \item Linear Regression
                    \item Stepwise Regression
                    \item Ridge Regression for suspected multicolinearity
                \end{itemize}

@@

                \begin{displaymath}
                   S_{1_i} = \left\{
                     \begin{array}{lr}
                       \text{where } f_i \geq d_i & :  \frac{f_i - d_i}{f_i} \times k  \\
                       \text{where } d_i > f_i  & : \frac{f_i-d_i }{\sigma_i^2} \times k
                     \end{array}
                   \right] \text{   , calculate quality score for each app $i$}
                \end{displaymath} 
                where
                \begin{itemize}
                    \item $S_{1_i}$ is the quality score for Application ID $i$
                    \item $n$ is the number of Application IDs
                    \item $d_i$ is the actual PROD defects for Application ID $i$
                    \item $f_i$ is the function to predict PROD defects for Application $i$ based upon 
                        \textit{UAT Defects}, \textit{SIT Defects}, \textit{Testing Effort}, 
                        and \textit{Development Effort}
                    \item $\sigma_i^2$ is the estimated variance for Application $i$
                \end{itemize}

@@

                \[
                    S_{1} = \sum\limits^n_{i=1} w'_i S_{1_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
                \]
                where
                \begin{itemize}
                    \item $S_1$ is the combined quality score for all Application IDs, 
                    a weighted average
                \end{itemize}

@@

        \subsubsection{AVAILABILITY}
            All the new requirements and great quality do not matter if the software is not available.
            All the new features and great quality do not matter if the software is not available.  Thus it
            is essential to set an expected Service Level Agreement (SLA)\footnote{For an SDO, the SLA is a 
            contract specifying the amount of time software will be available during a
            given time period. } and measure 
            performance against that SLA.  The following section will outline to data needed to properly
            calculate an SLA and the data needed to calculate the CRI score for availability.

            Special Note: The Service ID for availability does not have to be the same
            as the Application ID for quality or any of the other elements.  Some 
            organizations have a one-to-one mapping between Applications being developed
            and services being deployed.  Others have more complex sceranios that require
            multiple applications to be combined to form a service.  Then the availability
            of the system is tracked.

            \paragraph{AVAILABILITY DATA}
                Table \ref{tab:availdata} identifies the necessary data to calculate
                the CRI element score for availability.  Notice the three optional 
                fields: \textit{Uptime}, \textit{Scheduled Downtime}, and 
                \textit{Unscheduled Downtime}; they are optional because they can be
                used to calculated the \textit{Percent Uptime}.  The \textit{Percent Uptime}
                is the important value for the CRI schedule score.  Here are the two common
                approaches for calculating percent uptime:

@@

                \begin{itemize}
                    \item $S_{2_i}$ is the availability score for System ID $i$
                    \item $A_{a_i}$ actual availability for System ID $i$
                    \item $A_{e_i}$ expected availability for System ID $i$
                \end{itemize}

@@

                \[
                    S_{2} = \sum\limits^n_{i=1} w'_i S_{2_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
                \]
                where $S_2$ is the CRI availability score for the time frequency.

@@

                \begin{description}
                \item[Text] \hfill \\
                    The specific text used in the questions or statments
                    is very important.  The text cannot be too vague.  Also, the text
                    must be clear enough to eliminate misinterpretation. Survey
                    questions must be complete and not include gaps.  For example, if
                    an age range is presented, it must include all possible ages.  These
                    are just some of the difficulties with getting the text correct
                    in surveys. 
                \item[Number and Ordering] \hfill \\
                    The number of questions is important.  Too many questions and the 
                    respondents will lose interest and begin responding without the
                    adequate attention needed.  Plus, if the survey is too long there
                    is the risk of quitting before completion.  A short survey might
                    not cover the adequate amount of material.  Both short and long
                    surveys run the risk of providing inaccurate responses.  After
                    determining the best number of questions, the ordering of the questions
                    is important.  Previous survey questions can have an unintended 
                    impact on responses.  Thus, the ordering of questions needs to be
                    addressed. 
                \item[Sampling] \hfill \\
                    Next is the issue of sampling.  Not every customer can be surveyed, so 
                    sample sets os customers need to be presented with a survery.  
                    In the case of CRI, there are 2 possible scenarios for sampling.  
                    \begin{description}
                    \item[First]
                    When an SDO is part of a larger organization, there typically is
                    a small number of business partners that help to guide and 
                    direct the work performed by the SDO.  In this case, the business 
                    partners might be the the ones offering survey responses and they 
                    should all be willing to respond.  Thus, those business partners 
                    represent the entire population, and the surveys should result in 
                    a 100\% response rate which is technically a census.  
                    The only bias that will be present here is the bias of the business 
                    partners and sampling cannot control for that.

@@

            For more on creating appropriate surveys, see \cite{Snijkers2013} by Snijkers,
            Haraldsen, Jones, and Willimack. In the book, Snijkers et al. present a framework
            named generic statistical business process model (GSBPM) for conducting surveys
            in a business or organizational setting.  GSBPM covers the issues above as well
            as a few more issues such as response storage and risks.  Also, Cowles and Nelson
            provide another good resource for preparing and conducting surveys 
            \cite{Cowles2015}.  They even include an entire chapters on both writing 
            survey questions and survey errors.

@@

                \begin{itemize}
                    \item $S_{3_i}$ is the satisfaction score for Question ID $i$
                    \item $a_{ij}$ answer to question $i$ for respondent $j$
                    \item $n$ number of questions
                    \item $m$ number of respondents
                    \item $min$ minimum score for a question
                    \item $max$ maximum score for a question
                \end{itemize}

@@

                \[
                    S_{3} = \sum\limits^n_{i=1} w'_i S_{3_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
                \]
                where $S_3$ is the CRI satisfaction score for the time frequency.

@@

                \begin{displaymath}
                    \Delta_i = \frac{F_{a_i} - F_{s_i}}{ F_{s_i} - B_{s_i} + 1}
                \end{displaymath}
                where
                \begin{itemize}
                    \item $F_{a_i}$ the actual finish date of project $i$
                    \item $F_{s_i}$ the scheduled finish date of project $i$
                    \item $B_{s_i}$ the scheduled beginning date of project $i$
                    \item $\Delta_i$ the percent the schedule was missed for project $i$
                \end{itemize}

                Once all the $\Delta_i$'s have been determined, a distribution must
                be fit to the data. There are several techniques for testing the fit
                of a distribution: histograms, chi-square, Kolmogorov-Smirnov, Shapiro-Wilk,
                or Anderson-Darling \cite{Damodaran2015,Kutner2003}.
                The distribution is needed for the Cumulative
                Distribution Function (C.D.F.). The C.D.F. maps the values
                to a percentile rank within the distribution \cite{Downey2011}.
                The C.D.F. will be transformed to create
                the schedule score for CRI. Since all C.D.F. functions fall within the
                range $[0,1]$, the function needs to be shifted to center around 0, and then
                doubled to fill the desired range of $[-1,1]$. Thus the CRI schedule score
                for each project becomes the following.

                \begin{equation}
                \label{eq:CDF}
                    S_{4_i} = 2k \cdot (C.D.F.(\Delta_i) - \frac{1}{2})
                \end{equation}
                where
                \begin{itemize}
                    \item $S_{4_i}$ is the schedule score for Project ID $i$
                \end{itemize}

@@

                \[
                    S_{4} = \sum\limits^n_{i=1} w'_i S_{4_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
                \]
                where $S_4$ is the CRI schedule score for the time frequency.

@@

                Find the average of the $\Delta_i$'s.  This is the average percent of a missed
                schedule.  
                \begin{displaymath}
                   \bar{\Delta}  = \frac{\sum^n_{i=1}\Delta_i}{n}
                \end{displaymath}

@@

                After the $\bar{\Delta}$ is calculated, the following formulas are used to create the schedule scores
                for each project and then the averaged schedule score.

@@

                \[
                    S_{4} = \sum\limits^n_{i=1} w'_i S_{4_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1 \text{   , average the schedule scores}
                \]
                where
                \begin{itemize}
                    \item $n$ is the number of projects
                    \item $F_{a_i}$ the actual finish date of project $i$
                    \item $F_{s_i}$ the scheduled finish date of project $i$
                    \item $B_{s_i}$ the scheduled beginning date of project $i$
                    \item $\Delta_i$ the percent the schedule was missed
                    \item $\bar{\Delta}$ is the average percent schedules are missed
                    \item $S_{4_i}$ is the schedule score for project $i$
                \end{itemize}
                Again, this was just an alternate approach to scoring schedule.  
                It will not be used in the case studies.

@@

            To summarize, this element is not completely a measurement of requirements
            but rather a measurment of the work being completed.

@@

            \paragraph{REQUIREMENTS FORMULA}
                The requirements formula is the percentage above or below the
                scheduled number of requirements. Requirements have a nice
                lower bound of 0 since negative requirements cannot be 
                completed\footnote{Theoritically, a negative requirement would
                be considered a defect.}.  Unforntunately, an upper bound
                does not exist.  The variablity of requirements is not
                as large as the variability of the number of defects, so
                a simpler strategy can be used.  For requirements, a 
                multiplier $b$ will be used to find the upper bound. The
                number of scheduled requirements should be multiplied by
                $b$ to obtain the upper bound.  The value of $b$ should
                be determined by looking at the historical data to make sure
                no number of completed requirements will exceed $b$ times
                the number of scheduled requirements. An example will be shown
                in Section \ref{sec:case-req}. Common choices for $b$ will be 1
                and 2. Also, the formula will be
                created to deal with a value going above the upper bound.

                \begin{displaymath}
                   S_{5_i} = \left\{
                     \begin{array}{lr}
                       \text{where } R_{a_i} > b \times R_{s_i} & :  1 \times k \\
                       \text{where } R_{a_i} \leq R_{s_i} & : \left[ \frac{R_{a_i} - R_{s_i}}{R_{s_i}}\times k \right] \\
                       \text{where } R_{a_i} > R_{s_i}  & : \left[ \frac{R_{a_i} - R_{s_i} }{b \cdot R_{s_i}}\times k \right]
                     \end{array}
                   \right. \text{   , calculate requirements score for each project $i$}
                \end{displaymath}
                where
                \begin{itemize}
                    \item $S_{5_i}$ is the requirements score for Project ID $i$
                    \item $R_{a_i}$ actual requirements completed for Project ID $i$
                    \item $R_{s_i}$ expected requirements completed for Project ID $i$
                    \item $b$ multiplier to determine the upper bound
                \end{itemize}
                Then the requirements score is calculated as below.  
                Use a weighted average to combine the requirements scores
                from the Project IDs.

                \[
                    S_{5} = \sum\limits^n_{i=1} w'_i S_{5_i} \text{ where }
                        \sum\limits^n_{i=1} w'_i = 1
                \]

                where $S_5$ is the CRI requirements score for the time frequency.

@@

        It is impossible to know which or if correlations will always exist.  Thus it is necessary to
        check for correlations after determining element and overall CRI scores.  
        If correlation is determined, the element should not be dropped but rather be weighted less than
        the other elements.  This technique keeps the most data available but lessens the importance of
        the correlated element.

    \subsection{SENSITIVITY OF CRI}
    \label{sec:sensitivity}
        The sensitivity of the formulas should be tested as the scores should not
        flucate drastically for similar values.  There are 2 possible techniques
        for testing the sensitivity of the formulas. 
        \begin{description}
            \item[First] Given the historical data that has been collected,
                alter the values by some small random amount.  Then recalculate
                the CRI element score and compare with the original score.  This
                technique can be repeated many times in order to verify
                small changes do not largely affect the score.  Thus, a 
                formula which is not overly sensitive. 
            \item[Second] Another technique is to use Monte Carlo methods to 
                randomly generate input values for the element functions.  
                This can be done by finding the distributions of the historical
                data, and randomly selecting from that distribution.  If historical
                data is not available, then For more on sensitivity analysis 
                in statistical modeling, see \cite{Saltelli2000}.
        \end{description}

@@

        \subsubsection{CRI VS. FOCUS AREAS OF SOFTWARE ANALYTICS}
            Also, section \ref{subsub:softwareanalytics} mentions 3 important questions that
            software analytics must address.  Table \ref{tab:questions} presents the 3 questions
            and a description of how CRI addresses that specific question.  It is clear
            that CRI addresses the questions.  CRI is a beneficial technique of software
            analytics when applied to SDOs.

@@

                How much better is my model performing than a naive strategy, such as guessing? & CRI 
                provides consistency which may not exist without it.  Therefore, CRI removes the 
                guesswork of measuring an SDO. \\
                \myrowcolour%
                How practically significant are the results? & The CRI score is consistent
                and easy to comprehend.  Thus comparison with past performance is quick 
                and simple.  This is a significant advantage for software 
                development organizations. \\
                How sensitive are the results to small changes in one or more of the inputs? & 
                The question was extensively addressed in section \ref{sec:sensitivity}.  It appears CRI is
                not overly sensitive to small changes in the inputs.\\

>>>>

    The scores for CRI will range from -1, indicating the worst 
    performance, all the way to +1, indicating perfection.
    A score of 0 is an indication of meeting the basic expectations. 
    A negative score indicates worse-than-expected performance and a 
    positive score indicates better-than-expected performance.   Here are some 
    examples. An CRI score of 0.35 means the organization is 
    performing 35\% better than expected.  Conversely, a score 
    of -0.15 means an organization is performing 15\% worse than expected.

    Below are the attributes of the CRI scoring.
    \begin{itemize}
        \item The range of scores must have equal values above and below 0
        \item The minimum score must equate to the worst possible 
            performance, however that is defined
        \item Similarly, the maximum score must equate to the best possible performance.  
        \item A score of 0 must be average (or expected) performance
        \item All individual elements must have the same scoring range
    \end{itemize}

@@

    \subsection{ELEMENTS OF CRI}
        Each of the 5 elements of CRI has its own set of data that needs to
        be collected and formula for calculating a score. 
        These five elements will be outlined in the next sections.

@@

            \paragraph{QUALITY DATA}
                In order to properly score the quality of an SDO,
                certain data needs to be obtained in order to measure
                performance. Table \ref{tab:qualitydata} identifies
                the columns of data that will be used to create
                a score for the quality element of CRI.  
                Each column is classified as \textit{required} or
                \textit{optional}.  This is to allow some flexibility
                in the model for organizations that collect
                varying amounts of data.

@@

                The development and testing effort can come from any of 
                the following choices for effort. It is possible
                that other measures will work for effort.
                \begin{description}
                    \item[Actual Time] This number is a representation of the 
                        total amount of time spent on a project.  This number
                        can be measured in any unit of time: hours, days, weeks,
                        etc.  Actual time can be applied to development or testing
                        effort.
                    \item[Estimated Time] This number is a representation of the 
                        initial estimated amount of time spent on a project.  This number
                        can be measured in any unit of time: hours, days, weeks,
                        etc.  Estimated time can be applied to development or testing
                        effort.  It is common for the estimated and actual times
                        to be different.
                    \item[SLOC]  This number is the count of 
                        the total number of lines of source code for a project. 
                        Obviously, 
                        this item only counts as a level of
                        effort for development unless coding in used to generate
                        automated test cases. \footnote{Automated testing is the
                        process of creating software to automatically run tests
                        against other software.  The adoption of automated testing
                        is varied and it is not a solution in all cases 
                        \cite{Ramler2006}. }
                    \item[Modified Lines Of Code] This number is a count of the number 
                        of modified lines of source code. Modified lines is 
                        defined as the number of deleted, added, and modified 
                        lines of source code.  This number is different from above
                        since it does not include all the lines of source code.  Similar
                        to above, this number makes more sense for development effort.
                    \item[Test Cases] A test case is a step or series of steps followed
                        to validate some expected outcome of software.  Organizations
                        will create a number of test cases to be validated for a
                        software system.  The number of such test cases could
                        be used as a level of testing effort.
                \end{description}

@@

            \paragraph{QUALITY FORMULA}
                The first step in creating a score for the quality
                element is analysis of the historical data to create
                a baseline function.  The historical
                data is all quality data collected before  a given point
                in time.  Some common historical cutoffs are the current date
                or the end of the previous fiscal year.  Then a mathematical
                model, called the \textit{baseline quality function},
                to predict PROD Defects will be produced.  In statistical
                terms, the response is \textit{PROD Defects} and the predictors
                are: \textit{UAT Defects}, \textit{SIT Defects}, 
                \textit{Testing Effort}, and \textit{Development Effort}.  
                Some of the following strategies to find  
                a reasonable model include:
                \begin{itemize}
                    \item Removal of outliers and/or influential points
                    \item Linear Regression
                    \item Stepwise Regression
                    \item Ridge Regression for suspected multicolinearity
                \end{itemize}

@@

                \begin{displaymath}
                   S_{1_i} = \left\{
                     \begin{array}{lr}
                       \text{where } f_i \geq d_i & :  \frac{f_i - d_i}{f_i} \times k  \\
                       \text{where } d_i > f_i  & : \frac{f_i-d_i }{\sigma_i^2} \times k
                     \end{array}
                   \right] \text{   , calculate quality score for each app $i$}
                \end{displaymath} 
                where
                \begin{itemize}
                    \item $S_{1_i}$ is the quality score for Application ID $i$
                    \item $k$ scaling factor to produce results in the range $[-k,k]$
                    \item $n$ is the number of Application IDs
                    \item $d_i$ is the actual PROD defects for Application ID $i$
                    \item $f_i$ is the function to predict PROD defects for Application $i$ based upon 
                        \textit{UAT Defects}, \textit{SIT Defects}, \textit{Testing Effort}, 
                        and \textit{Development Effort}
                    \item $\sigma_i^2$ is the estimated variance for Application $i$
                \end{itemize}

@@

                \[
                    S_{1} = \sum\limits^n_{i=1} w_i S_{1_i}
                \]
                where
                \begin{itemize}
                    \item $S_1$ is the combined quality score for all Application IDs, 
                    a weighted average
                    \item $w_i > 0$ for all $i$
                    \item $\sum\limits^n_{i=1} w_i = 1$
                \end{itemize}

@@

        \subsubsection{AVAILABILITY}
            All the new requirements and great quality do not matter if the software is not available.
            Thus it
            is essential to set an expected Service Level Agreement (SLA)\footnote{For an SDO, the SLA is a 
            contract specifying the amount of time software will be available during a
            given time period. } and measure 
            performance against that SLA.  The following section will outline the data needed to properly
            calculate an SLA and to calculate the CRI score for availability.

            Special Note: The Service ID for availability does not have to be the same
            as the Application ID for quality or any of the other elements.  Some 
            organizations have a one-to-one mapping between Applications being developed
            and services being deployed.  Others have more complex scenarios that require
            multiple applications to be combined to form a service.  Then the availability
            of the system is tracked.

            \paragraph{AVAILABILITY DATA}
                Table \ref{tab:availdata} identifies the necessary data to calculate
                the CRI element score for availability.  Notice the three optional 
                fields: \textit{Uptime}, \textit{Scheduled Downtime}, and 
                \textit{Unscheduled Downtime}; they are optional because they can be
                used to calculate the \textit{Percent Uptime}.  The \textit{Percent Uptime}
                is the important value for the CRI schedule score.  Here are the two common
                approaches for calculating percent uptime:

@@

                \begin{itemize}
                    \item $S_{2_i}$ is the availability score for System ID $i$
                    \item $k$ scaling factor to produce results in the range $[-k,k]$
                    \item $A_{a_i}$ actual availability for System ID $i$
                    \item $A_{e_i}$ expected availability for System ID $i$
                \end{itemize}

@@

                \[
                    S_{2} = \sum\limits^n_{i=1} w_i S_{2_i} 
                \]
                where
                \begin{itemize}
                    \item $S_2$ is the combined availability score for all Service IDs, 
                    a weighted average
                    \item $w_i > 0$ for all $i$
                    \item $\sum\limits^n_{i=1} w_i = 1$
                \end{itemize}

                Then $S_2$ represents the CRI availability score for that given time 
                frequency.

@@

                \begin{description}
                \item[Text] \hfill \\
                    The specific text used in the questions or statements
                    is very important.  The text cannot be too vague.  Also, the text
                    must be clear enough to eliminate misinterpretation. Survey
                    questions must be complete and not include gaps.  For example, if
                    an age range is presented, it must include all possible ages.  These
                    are just some of the difficulties with getting the text correct
                    in surveys. 
                \item[Number and Ordering] \hfill \\
                    The number of questions is important.  Too many questions and the 
                    respondents will lose interest and begin responding without the
                    adequate attention needed.  Plus, if the survey is too long there
                    is the risk of quitting before completion.  A short survey might
                    not cover the adequate amount of material.  Both short and long
                    surveys run the risk of providing inaccurate responses.  After
                    determining the best number of questions, the ordering of the questions
                    is important.  Previous survey questions can have an unintended 
                    impact on responses.  Thus, the ordering of questions needs to be
                    addressed. 
                \item[Sampling] \hfill \\
                    Next is the issue of sampling.  Not every customer can be surveyed, so 
                    sample sets of customers need to be presented with a survey.  
                    In the case of CRI, there are 2 possible scenarios for sampling.  
                    \begin{description}
                    \item[First]
                    When an SDO is part of a larger organization, there typically is
                    a small number of business partners that help to guide and 
                    direct the work performed by the SDO.  In this case, the business 
                    partners might be the the ones offering survey responses and they 
                    should all be willing to respond.  Thus, those business partners 
                    represent the entire population, and the surveys should result in 
                    a 100\% response rate which is technically a census.  
                    The only bias that will be present here is the bias of the business 
                    partners and sampling cannot control for that.

@@

            For more on creating appropriate surveys, see \cite{Snijkers2013} by Snijkers,
            Haraldsen, Jones, and Willimack. They present a framework
            named generic statistical business process model (GSBPM) for conducting surveys
            in a business or organizational setting.  GSBPM covers the issues above as well
            as a few more issues such as response storage and risks.  Also, Cowles and Nelson
            provide another good resource for preparing and conducting surveys 
            \cite{Cowles2015}.  They even include entire chapters on both writing 
            survey questions and survey errors.

@@

                \begin{itemize}
                    \item $S_{3_i}$ is the satisfaction score for Question ID $i$
                    \item $k$ scaling factor to produce results in the range $[-k,k]$
                    \item $a_{ij}$ answer to question $i$ for respondent $j$
                    \item $n$ number of questions
                    \item $m$ number of respondents
                    \item $min$ minimum score for a question
                    \item $max$ maximum score for a question
                \end{itemize}

@@

                \[
                    S_{3} = \sum\limits^n_{i=1} w_i S_{3_i}
                \]
                where
                \begin{itemize}
                    \item $S_3$ is the combined satisfaction score for all Questions IDs, 
                    a weighted average
                    \item $w_i > 0$ for all $i$
                    \item $\sum\limits^n_{i=1} w_i = 1$
                \end{itemize}

                Then $S_3$ represents the CRI satisfaction score for that given time 
                frequency.

@@

                \begin{displaymath}
                    \Delta_i = \frac{F_{a_i} - F_{s_i}}{ F_{s_i} - B_{s_i} + 1}
                \end{displaymath}
                where
                \begin{itemize}
                    \item $F_{a_i}$ the actual finish date of project $i$
                    \item $F_{s_i}$ the scheduled finish date of project $i$
                    \item $B_{s_i}$ the scheduled beginning date of project $i$
                    \item $\Delta_i$ the proportion the schedule was missed for project $i$
                \end{itemize}

                Once all the $\Delta_i$'s have been determined, a distribution must
                be fit to the data. There are several techniques for testing the fit
                of a distribution: histograms, chi-square, Kolmogorov-Smirnov, Shapiro-Wilk,
                or Anderson-Darling \cite{Damodaran2015,Kutner2003}.
                The distribution is needed for the Cumulative
                Distribution Function (CDF) 
                \nomenclature{CDF}{Cumulative Distribution Function}. 
                The CDF maps the values
                to a percentile rank within the distribution \cite{Downey2011}.
                The CDF will be transformed to create
                the schedule score for CRI. Since all CDF functions fall within the
                range $[0,1]$, the function needs to be shifted to center around 0, and then
                doubled to fill the desired range of $[-1,1]$. Thus the CRI schedule score
                for each project becomes the following.

                \begin{equation}
                \label{eq:CDF}
                    S_{4_i} = 2k \cdot (CDF(\Delta_i) - \frac{1}{2})
                \end{equation}
                where
                \begin{itemize}
                    \item $S_{4_i}$ is the schedule score for Project ID $i$
                    \item $k$ scaling factor to produce results in the range $[-k,k]$
                \end{itemize}

@@

                \[
                    S_{4} = \sum\limits^n_{i=1} w_i S_{4_i}
                \]
                where
                \begin{itemize}
                    \item $S_4$ is the combined schedule score for all Project IDs, 
                    a weighted average
                    \item $w_i > 0$ for all $i$
                    \item $\sum\limits^n_{i=1} w_i = 1$
                \end{itemize}

                Then $S_4$ represents the CRI schedule score for that given time 
                frequency.

@@

                Find the average of the $\Delta_i$'s.  This is the average proportion of a missed
                schedule.  
                \begin{displaymath}
                   \bar{\Delta}  = \frac{\sum^n_{i=1}\Delta_i}{n}
                \end{displaymath}

@@

                After $\bar{\Delta}$ is calculated, the following formulas are used to create the schedule scores
                for each project and then the averaged schedule score.

@@

                \[
                    S_{4} = \sum\limits^n_{i=1} w_i S_{4_i} 
                \]
                where
                \begin{itemize}
                    \item $S_4$ is the combined schedule score for all Project IDs, 
                    a weighted average
                    \item $k$ scaling factor to produce results in the range $[-k,k]$
                    \item $w_i > 0$ for all $i$
                    \item $\sum\limits^n_{i=1} w_i = 1$
                    \item $n$ is the number of projects
                    \item $F_{a_i}$ the actual finish date of project $i$
                    \item $F_{s_i}$ the scheduled finish date of project $i$
                    \item $B_{s_i}$ the scheduled beginning date of project $i$
                    \item $\Delta_i$ the percent the schedule was missed
                    \item $\bar{\Delta}$ is the average percent schedules are missed
                    \item $S_{4_i}$ is the schedule score for project $i$
                \end{itemize}
                Then $S_4$ represents the CRI schedule score for that given time 
                frequency.
                Again, this was just an alternate approach to scoring schedule.  
                It will not be used in the case studies.

@@

            To summarize, this element is not completely a measurement of requirements
            but rather a measurement of the work being completed.

@@

            \paragraph{REQUIREMENTS FORMULA}
                The requirements formula is the percentage above or below the
                scheduled number of requirements. Requirements have a nice
                lower bound of 0 since negative requirements cannot be 
                completed\footnote{Theoritically, a negative requirement would
                be considered a defect.}.  Unfortunately, an upper bound
                does not exist.  The variability of requirements is not
                as large as the variability of the number of defects, so
                a simpler strategy can be used.  For requirements, a 
                multiplier $b$ will be used to find the upper bound. The
                number of scheduled requirements should be multiplied by
                $b$ to obtain the upper bound.  The value of $b$ should
                be determined by looking at the historical data to make sure
                no number of completed requirements will exceed $b$ times
                the number of scheduled requirements. An example will be shown
                in Section \ref{sec:case-req}. Common choices for $b$ will be 1
                and 2. Also, the formula will be
                created to deal with a value going above the upper bound.

                \begin{displaymath}
                   S_{5_i} = \left\{
                     \begin{array}{lr}
                       \text{where } R_{a_i} > b \times R_{s_i} & :  1 \times k \\
                       \text{where } R_{a_i} \leq R_{s_i} & : \left[ \frac{R_{a_i} - R_{s_i}}{R_{s_i}}\times k \right] \\
                       \text{where } R_{a_i} > R_{s_i}  & : \left[ \frac{R_{a_i} - R_{s_i} }{b \cdot R_{s_i}}\times k \right]
                     \end{array}
                   \right. \text{   , calculate requirements score for each project $i$}
                \end{displaymath}
                where
                \begin{itemize}
                    \item $S_{5_i}$ is the requirements score for Project ID $i$
                    \item $k$ scaling factor to produce results in the range $[-k,k]$
                    \item $R_{a_i}$ actual requirements completed for Project ID $i$
                    \item $R_{s_i}$ expected requirements completed for Project ID $i$
                    \item $b$ multiplier to determine the upper bound
                \end{itemize}
                Then the requirements score is calculated as below.  
                Use a weighted average to combine the requirements scores
                from the Project IDs.

                \[
                    S_{5} = \sum\limits^n_{i=1} w_i S_{5_i} 
                \]
                where
                \begin{itemize}
                    \item $S_5$ is the combined requirements score for all Project IDs, 
                    a weighted average
                    \item $w_i > 0$ for all $i$
                    \item $\sum\limits^n_{i=1} w_i = 1$
                \end{itemize}

                Then $S_5$ represents the CRI requirements score for that given time 
                frequency.

@@

        It is impossible to know which or if correlations will always exist.  Thus it is necessary to
        check for correlations after determining element and overall CRI scores.  
        If an element is determined to be correlated with another element, neither element should be dropped,
        but rather one of the elements should be weighted less than
        the other correlated element.  
        This technique keeps the most data available but lessens the importance of
        the correlated element.

    \subsection{SENSITIVITY OF CRI}
    \label{sec:sensitivity}
        The sensitivity of the formulas should be tested as the scores should not
        fluctuate drastically for similar values.  There are 2 possible techniques
        for testing the sensitivity of the formulas. 
        \begin{description}
            \item[First] Given the historical data that has been collected,
                alter the values by some small random amount.  Then recalculate
                the CRI element score and compare with the original score.  This
                technique can be repeated many times in order to verify
                small changes do not largely affect the score.  Thus, a 
                formula which is not overly sensitive. 
            \item[Second] Another technique is to use Monte Carlo methods to 
                randomly generate input values for the element functions.  
                This can be done by finding the distributions of the historical
                data, and randomly selecting from that distribution.  If historical
                data is not available, then the normal distribution can be used.
                See \cite{Saltelli2000} for more information on sensitivity analysis 
                in statistical modeling.
        \end{description}

@@

        \subsubsection{CRI VS. IMPORTANT QUESTIONS OF SOFTWARE ANALYTICS}
            Also, section \ref{subsub:softwareanalytics} mentions 3 important questions that
            software analytics must address.  Table \ref{tab:questions} presents the 3 questions
            and a description of how CRI addresses that specific question.  It is clear
            that CRI addresses the questions.  CRI is a beneficial technique of software
            analytics when applied to SDOs.

@@

                How much better is my model performing than a naive strategy, such as guessing? & CRI 
                provides consistency which may not exist without it.  Therefore, CRI removes the 
                guesswork of measuring an SDO. \\
                \myrowcolour%
                How practically significant are the results? & The CRI score is consistent
                and easy to comprehend.  Thus comparison with past performance is quick 
                and simple.  This is a significant advantage for software 
                development organizations. \\
                How sensitive are the results to small changes in one or more of the inputs? & 
                The question was extensively addressed in section \ref{sec:sensitivity}. CRI is
                not overly sensitive to small changes in the inputs.\\
